Assessing primitives performance\\ on multi-stage execution

### 2018-05-17 paper.tex
fix size 1000 on ubuntu

2   25.9913138   0.0320593050
3   24.868577   0.062229078
4   27.454826   0.044223466

@@

We can draw the following patterns from these results:
\begin{itemize}
\item The execution time of the Plugin implementations is either very close or greater than \sd{within which ranges? 10\% 200\%} the baseline's for the small strings.
\item The Slang+JIT implementation is more efficient than the baseline in every case. Nevertheless, the performance gap between this version and the PureSlang one tends to decrease as the string size increases. 
\item The compiler used (either GCC or LLVM) does not lead to significant differences in terms of performance, except for the 100+-characters strings. 
\end{itemize}

>>>>

2   25.35945   0.1742098
3   25.42575   0.1621165
4   26.76261   0.186075

@@

We can draw the following patterns from these results:
\begin{itemize}
\item The execution time of the Plugin implementations is either very close or greater than \sd{within which ranges? 10\% 200\%} the baseline's for the small strings.
\item The Slang+JIT implementation is more efficient than the baseline in every case. Nevertheless, the performance gap between this version and the PureSlang one \sk{all the Slang versions, in the end} tends to decrease as the string size increases. 
\item \sk{if we keep these results, then it actually leads to huge differences...} The compiler used (either GCC or LLVM) does not lead to significant differences in terms of performance, except for the 100+-characters strings. 
\end{itemize}
